---
title: "Coxon_HW2"
author: "Victoria Coxon"
date: "September 20, 2015"
output: html_document
---


# Homework 1

Guidelines: Homeworks should be clear and legible, with answers clearly indicated and work shown. Homeworks will be given a minus, check, or check plus owing to completion and correctness. You are welcome to work with others but please submit your own work. Your homework must be produced in an R Markdown (.rmd) file submitted via github. 

If you are having trouble accomplishing this, please refer to the [guide](http://spia.uga.edu/faculty_pages/tyler.scott/teaching/PADP8120_Fall2015/Homeworks/submitting_homework.shtml). 

This homework adapts materials from the work of Michael Lynch (http://spia.uga.edu/faculty_pages/mlynch/), Tyler McCormick (http://www.stat.washington.edu/~tylermc/), and Open Intro (https://www.openintro.org/stat/textbook.php)


## Problems

1. Being hit by a chair is a common occurrence in WWE professional wrestling. The number of people hit upside the head with chairs can vary from program to program. Suppose that the number of chair-bashings per program is Normally distributed, with mean thirty-five (35) bashings and standard deviation of eight (8) bashings. What is the probability that one WWE program will contain less than nineteen (19) bashings or more than forty (40) bashings?

```{r}
bashings.lowerpval <- pnorm(q=19,mean = 35, sd = 8, lower.tail = TRUE);bashings.lowerpval
bashings.upperpval <- pnorm(q=40,mean = 35, sd = 8, lower.tail = FALSE);bashings.upperpval
total.bashings <- bashings.lowerpval + bashings.upperpval; total.bashings
```
When seeking to determine the probability within one WWE program (1 sample) of chair-bashing observations(x) of x < 19 or x > 40, the combined probability of either obsrvation is  0.2887357 or 0.289.


2. A corporation has just received new machinery that must be installed and checked before it becomes operational. The following table shows a manager’s probability assessment for the number of days required before the machinery becomes operational:

| Days  | 5    | 6    | 7    | 8    | 9    | 10 |
|-------|------|------|------|------|------|----|
| Prob. | 0.06 | 0.21 | 0.37 | 0.20 | 0.13 | 0.06 |

Let A be the event “It will be more than 6 days before the machinery becomes operational,” and let B be the event “It will be less than 8 days before the machinery becomes available.”

  a. Find the probability of event A.
```{r}
A.event <- 0.37 + 0.20 + 0.13 + 0.06; print(A.event)
```
The probability of Event A, x > 6 days, is 0.76.  There is a relatively high probability that
the machinery will become operational after 6 days.

  b. Find the probability of event B.
```{r}
B.event <- 0.06 + 0.21 + 0.37; print(B.event)
```
The probability of Event B, x < 8 days, is 0.64.  There is a relatively high probability that
the machinery will become operational in under 8 days.

  c. Find the probability of the complement of event A.
```{r}
complement.A <- 1 - A.event; print(complement.A)
```
The probability that the machinery will be operational in under 6 days is 0.24.

  d. Find the probability of the intersection of events A and B. 
  
In all the listed probabilities for scenarios where the machinery becomes operational, this concerns the probability where 6 < x < 8.  This corresponds to 7 days, hence the probability
is 0.37.

  e. Find the probability of the union of events A and B.
```{r}
AandB.event <- A.event + B.event - 0.37; print(AandB.event)
```
The probability of both events A and B happening are equal to 1.  

3. An ultramarathon race official has found that 68% of first time entrants and 87% ofrepeat racers finish the race. Of all entrants, 64% are repeat racers and the remainders are first time entrants.

a. What is the probability that a randomly chosen entrant is a repeat racer who will eventually finish the race?
Prob(repeat and finish) = 0.87     Prob(repeat and quit) = 1 - 0.87 = 0.13
Prob(first and finish) = 0.68     Prob(first and quit) = 1 - 0.68 = 0.32
Prob(repeat) = 0.64            Prob(first) = 1 - 0.64 = 0.36
```{r}
Prob.repeat.and.finish <- 0.87
Prob.repeat <- 0.64
random.repeat.and.finish <- 0.87 * 0.64; print(random.repeat.and.finish)
```
P(random.repeat.and.finish) = 0.5568 or 0.557.

b. Find the probability that a randomly chosen entrant will eventually finish the race.
```{r}
Prob.first.and.finish <- 0.68
Prob.first <- 0.36
random.first.and.finish <- 0.68 * 0.36; print(random.first.and.finish)

random.finish <- random.repeat.and.finish + random.first.and.finish; print(random.finish)
```
The P(random.finish) = 0.8016 or 0.802.

c. What is the probability that a randomly chosen entrant either is a repeat racer or will eventually finish (or both)?
```{r}
repeat.or.finish <- Prob.repeat + random.finish - random.repeat.and.finish; print(repeat.or.finish)
```
The P(repeat.or.finish) = 0.8848 or 0.885.

4. A school received a grant to offer two extracurricular clubs, art and chess. Of the students 35% signed up for art club and 40% for chess club. Of those signing up for art club 20% signed up for chess club.
Prob(art) = 0.35
Prob(chess) = 0.40
Prob(chess given art) = 0.20

a. What is the probability that a randomly selected student signed up for both clubs?
```{r}
Prob.art <- 0.35
Prob.chess <- 0.40
Prob.chess.given.art <- 0.20
random.chess.given.art <- Prob.art * Prob.chess.given.art; print(random.chess.given.art)
```
The probability that a randomly selected student who signed up for chess club also signed up for art club is 0.07.

b. What is the probability that a randomly selected student who signed up for chess club also signed up for art club?
```{r}
random.chess.and.art <- random.chess.given.art / Prob.chess; print(random.chess.and.art)
```
The probability that a randomly selected student who signed up for chess club also signed up for art club is 0.175.

c. What is the probability that a randomly chosen student signed up for at least one of these two clubs? 
```{r}
two.clubs <- Prob.art + Prob.chess - random.chess.given.art; print(two.clubs)
```
The probability that a randomly chosen student signed up for at least one of these two clubs is 0.68.  

5. Records show that 442 students recently entered a Florida public school district. Of those 442, 84 have not received their vaccinations. The district’s physician is scheduled to go from school to school next Tuesday to give shots to those who need them. If we know that about 8% of students are absent on any given day, how many unvaccinated students are likely to miss the doctor visit?
```{r}
Prob.no.vac <- 84/442; print(Prob.no.vac)
(8 * 442) / 100 #35.36 kids
Prob.absent <- 35/442; print(Prob.absent)
84 * Prob.absent
```
P(no.vac) = 0.1900452    P(absent) = 0.07918552 = 0.08

Working from the assumption that having unvaccinated status is not related to absenteeism, then P(no.vac) has no bearing on the P(absent). The unvaccinated kids will have the same chance of being absent as the rest of the kids in the sample where n = 442. The number of kids the district's physician will miss is 6.651584 or 6 (because you cannnot have portions of kids; the variable is discrete).

6. For questions 1a - 1c, assume a variable is normally distributed with a mean of 180 and a standard deviation of 25. Please show all work (i.e., relevant code - hint: the `pnorm`/`qnorm`/`dnorm` family will be your friend here)

a. What is the probability that a single draw from this distribution, labeled X, will be greater than 210?
```{r}
#pnorm(CV,n,sd,lower.tail  = FALSE) -> if greater than mean 
#              lower.tail = TRUE) -> if less than mean
pnorm(210,180,25,lower.tail = FALSE)
```
The probabilty that a single draw where x > 210 from a normally distributed variable with a mean of 180 and a standard deviation of 25 is 0.1150697.

b. What is the probability that a single draw from this distribution, labeled Y, will be less than 182?
```{r}
pnorm(182,180,25,lower.tail = TRUE)
```
The probability that a single draw from this distribution, labeled Y, will be less than 182 is 0.5318814.

c. What is the probability that a single draw from this distribution, labeled Z, will be between 160 and 192?
```{r}
1- (pnorm(160,180,25,lower.tail = TRUE) + pnorm(192,180,25,lower.tail = FALSE))
```
The probability that a single draw from this distribution, labeled Z, will be between 160 and 192 is 0.4725309.

7. The random variable x has the discrete probability distribution shown here:


| x | -2    | -1    | 0    | 1    | 2    | 
|-------|------|------|------|------|------|
| p(x) | 0.15 | 0.15 | 0.35 | 0.25 | 0.10 |

a. Find $P(x<=0)$
```{r}
#Need to find sum of all p(x) values that are < or = to 0.
#P(x = -2) <- 0.15
#P(x = -1) <- 0.15
#P(x = 0)  <- 0.35
0.15 + 0.15 + 0.35
```
The probability of P(x<=0) is 0.65,

b. Find $P(x>-1)$
```{r}
#Need to find the sum of all the p(x) values that are > -1.
#P(x = 0) <- 0.35
#P(x = 1) <- 0.25
#P(x = 2) <- 0.10
0.35 + 0.25 + 0.10
```
The probability of P(x>-1) is 0.7.

c. Find $P(-1<=x<=1)$
```{r}
#Need to find the sum of all values p(x) between -1 and 1.
#P(x = -1) <- 0.15
#P(x = 0)  <- 0.35
#P(x = 1) <- 0.25
0.15 + 0.35 + 0.25
```
The probabilty of P(-1<=x<=1) is 0.75.

d. Find $P(x<2)$
```{r}
#Need to find the sum  of p(x) values < 2.
#P(x = 1) <- 0.25
#P(x = 0) <- 0.35
#P(x = -1) <- 0.15
#P(x = -2) <- 0.15
0.25 + 0.35 + 0.15 + 0.15
#Alternatively, I can also use 1 - P(x = 2).
#P(x = 2) <- 0.10
1 - 0.10
```
The probability of P(x<2) is 0.90.

e. Find $P(-1<x<2)$
```{r}
#Need to find the sum of all p(x) values between -1 and 2.
#P(x = 0)  <- 0.35
#P(x = 1) <- 0.25
0.35 + 0.25
#Alternatively I can also use 1 - [P(x = -1 ) + P(x = -2)] + [P(x = 2)]
#P(x = -2) <- 0.15
#P(x = -1) <- 0.15
#P(x = 2) <- 0.10
1 - (0.15 + 0.15 + 0.10)
```

The probability of $P(-1<x<2)$ is 0.60.

8. Consider a sequence of independent coin flips, each of which has probability $p$ of being heads. Define a random variable $X$ as the length of the run (either heads or tails) started by the first trial. (For example, $X=3$ if either TTTH or HHHT is observed.) Write the distribution of X and compute $E(X)$.

NOTE: HW2 Key states to skip this problem.

9. Consider flipping an unequally weighted coin with probability of success $.55$. Say that $X$ is the random variable associated with this coin and that $X=1$ if heads (success), 0 otherwise. Simulate 20 coin flips and store them as a variable called “cflip.” In R, do this with `cflip=rbinom(20,1,.55)`. Use `?rbinom` to make sure you understand what each part of the command stands for.

```{r}
?rbinom
#rbinom(n, size, prob)
cflip=rbinom(20,1,.55)
```

a. Take 20 samples with replacement from cflip and compute the mean of the sample. In R:

```{r}
?sample
#sample(x, size, replace = FALSE, prob = NULL)
#With replacement means replace = False will now be replace = TRUE
cflipsamp=sample(cflip,20,replace=T)
mean(cflipsamp)
sd(cflipsamp)
```

In a scenario where n = 20 samples with replacement, the mean is 0.7 with a sd = 0.4701623.  

b. Repeat step B (but not step A) 500 times, storing the mean of the sample each time. You could do this using a “for” loop to repeat the same step many times. An example of code for a loop is below. However, try to find a non-loop way of accomplishing the same thing (e.g., the `replicate` function). 
`resamp.mean=rep(NA,500) for(i in 1:500){ resamp.mean[i]<-mean(sample(cflip,20,replace=T))}`.

```{r}
?replicate
#replicate(n, expr, simplify = "array")
cflip.samp.500 <- replicate(500,mean(sample(cflip,20,replace=T))); print(cflip.samp.500)
mean(cflip.samp.500)
sd(cflip.samp.500)
hist(cflip.samp.500)
```
In a scenario where n = 500 samples with replacement, the mean is 0.6486 with a sd = 0.1093249.

c. Plot a histogram of the re-sampled means. Does it look like what we know from normal theory that the sampling distribution of the mean should look like in this case?

Yes, this confroms to what we woud expect from the Law of Large Numbers and Central Tendency.  
The distribution is approximately normal and distributed around the mean of 0.6486 with a sd = 0.1093249.

d. Experiment with increasing/decreasing the number of original samples (draws within one "sample") and the number of re-samples (number of times you repeat the sampling process). Pay attention to the impact changing either has on the resulting distribution of sample means, and provide some form of visual demonstration (table and/or figure) to show how sample size changes your results. 
```{r}
#I am unsure as to how I need to structure this. I am relying heavily on the HW2 Key and copying verbatim.
?par
#par(..., no.readonly = FALSE)
#Still don't get it...
par(mfrow=c(2,2))
##GUIDE:  hist(replicate(# of repeats, mean(sample(x,# of draws, replace = TRUE if w/replacement)))main='Label of Histogram',xlab='')

# 20 draws repeated 20 times
hist(replicate(20,mean(sample(cflip,20,replace=T))),main='20d, 20s',xlab='')
```
This distribution is not normaally distributed  but it would not be expected to be normally distribued as the n < 30.
```{r}
# 20 draws repeated 500 times
hist(replicate(500,mean(sample(cflip,20,replace=T))),main='20d, 500s',xlab='')
```
This distribution is a much better candidate for the normality assumption because the n > 30.  Interestingly, when looking at this histogram in comparison to the 500d,500s histogram below, the lower number of draws results in a less precise/more variability/higher sd from the mean. In short, the 20d,500s has much greater spread as opposed to the tighter distribution around the mean in 500d,500s. However, this is not necessarily a bad thing; it can be a more inclusive representation of the p(x) drawn at random. Unfortunately, this is not the case in this population where the real  mean N[p(x)] = 0.55.  
```{r}
# 500 draws repeated 20 times
hist(replicate(20,mean(sample(cflip,500,replace=T))),main='500d, 20s',xlab='')
```
```{r}
# 500 draws repeated 500 times
hist(replicate(500,mean(sample(cflip,500,replace=T))),main='500d, 500s',xlab='')
```

10. Consider a population of donuts with with an average survival time until becomming stale of $\mu = 3$ days and a standard deviation of failure times $\sigma = .25$ days (exponential distribution). If you take a sample of 24 donuts, what are the chances the mean failure time of your sample will be:

(a) Greater than 3 days? 
```{r}
?pexp
#dexp(x, rate = 1, log = FALSE)   -> dexp gives the density
#pexp(q, rate = 1, lower.tail = TRUE, log.p = FALSE)    -> pexp gives the distribution function
#qexp(p, rate = 1, lower.tail = TRUE, log.p = FALSE)     -> qexp gives the quantile function
#rexp(n, rate = 1/rate)     ->  rexp generates random deviates
#Let's use rexp...
#Looking for mean failure time...
mean(rexp(100000,1/3))
#The mean is 2.987443.
```
Because we are interested in finding the instances where $\mu > 3$ days, it requires looking  at the upper tail of the normal distribution (lower.tail = FALSE).  The question asks about the probability distribution of $\mu > 3$ days, it makes sense to use "pexp ".
```{r}
#pexp(q, rate = 1, lower.tail = TRUE, log.p = FALSE)
pexp(3,rate = 1/3, lower.tail = FALSE)
```
The mean failure time where $mu > 3$ days given a 24 donut sample is  0.3678794.

(b) Less than 1.5 days?
```{r}
#Need to look at the lower tail of the distribution (lower.tail = TRUE)
pexp(1.5,rate = 1/3, lower.tail = TRUE)
```
The mean failure time where $mu < 1.5$ days given a 24 donut sample is 0.3934693.

(c) Between 2.25 and 3.75 days?
```{r}
# Need to find the area between the tails; 1 - [pexp(q, rate = ..., lower.tail = TRUE) - pexp(q,rate = ..., lower.tail = FALSE)
1- pexp(2.25,rate = 1/3, lower.tail = TRUE) - pexp(3.75,rate = 1/3, lower.tail = FALSE) 
```
The mean failure time where $2.25 < mu < 3.75$ days given a 24 donut sample is 0.1858618.

11. (also problem 4.17/4.18 in Open Intro 3) Identify hypotheses, For each item, write the null and alternative hypotheses in words and then symbols for each of the following situations.

a. New York is known as \the city that never sleeps". A random sample of 25 New Yorkers were asked how much sleep they get per night. Do these data provide convincing evidence thatNew Yorkers on average sleep less than 8 hours a night?

Null: New Yorkers sleep eight hours per night on average.
Alternative: New Yorkers sleep less than eight hours per night on average.
$H0: mu = 8$
$HA: mu < 8$

b. Employers at a firm are worried about the effect of March Madness, a basketball championship held each spring in the US, on employee productivity. They estimate that on a regular business day employees spend on average 15 minutes of company time checking personal email, making personal phone calls, etc. They also collect data on how much company time employees spend on such non-business activities during March Madness. They want to determine if these data provide convincing evidence that employee productivity decreases during March Madness.

Null: Employees use 15 minutes of time per day engaged in non-business  activities during March.
Alternative: Employees use more than 15 minutes of time per day engaged in non-business  activities during March.
$H0: mu = 15$
$HA: mu > 15$

c. Since 2008, chain restaurants in California have been required to display calorie counts of each menu item. Prior to menus displaying calorie counts, the average calorie intake of diners at a restaurant was 1100 calories. After calorie counts started to be displayed on menus,a nutritionist collected data on the number of calories consumed at this restaurant from a random sample of diners. Do these data provide convincing evidence of a difference in the average calorie intake of a diners at this restaurant?

Null: Calorie consumption after the implementation of the calore count requirement is the same as before the requirement.  
Alternative: Calore consumption after the implementation of the calore count requirement is NOT the same as before the requirement.  
$H0: mu = 1100$
$HA: mu != 1100$

d. Based on the performance of those who took the GRE exam between July 1, 2004 and June 30, 2007, the average Verbal Reasoning score was calculated to be 462. In 2011 the average verbal score was slightly higher. Do these data provide convincing evidence that the average GRE Verbal Reasoning score has changed since 2004?

Null: There has been no change in the average GRE Verbal Reasoning Score since 2004.
Alternative: There has been a change in the average GRE Verbal Reasoning Score since 2004.
$H0: mu = 462$
$HA: mu != 462$

12. (also 4.30 in Open Intro 3) A food safety inspector is called upon to investigate a restau-rant with a few customer reports of poor sanitation practices. The food safety inspector uses a hypothesis testing framework to evaluate whether regulations are not being met. If he decides the restaurant is in gross violation, its license to serve food will be revoked.

a. Write the hypotheses in words.

Null: The restaurant is NOT is gross violation of sanitation regulations.
Alternative: The restarant is in gross violation of sanitation regulations.

b. What is a Type 1 Error in this context?

In this context, a Type I Error would be concluding that the restuarant is in gross violation of sanitation regulations when it actually is not. This could be a function of setting the critical value/signficance level too low.

c. What is a Type 2 Error in this context?

In this context, a Type II Error would be concluding that the restuarant is not in gross violation of sanitation regulations when it actually is.  This could be the result of setting the critical value/significance level too high.

d. Which error is more problematic for the restaurant owner? Why?

A Type I Error would be more immediately problematic for the restaurant owner because a finding of gross violation of sanitation regulations would result in an immediate (but hopefully temporary) closure of the restaurant until the offending issue(s) are remedied. The owner  would lose revenues and expend monies to fix a problem that should not have been indicated.

e. Which error is more problematic for the diners? Why?'
A Type II Error would be more immediately problematic for the diners at the restuarant because a finding that the restuarant is not in  violation of sanitation regulations would likely result  in more food-borne illness like food poisoning (which may be fatal to specific vulnerable populations).  The restuarant should be closed  to remedy the violations but is still open for business and is a public health threat.

### Report your process

You're encouraged to reflect on what was hard/easy, problems you solved, helpful tutorials you read, etc. Give credit to your sources, whether it's a blog post, a fellow student, an online tutorial, etc.


### Rubric


Minus: Didn't tackle at least 3 tasks. Or didn't make companion graphs. Didn't interpret anything but left it all to the "reader". Or more than one technical problem that is relatively easy to fix. It's hard to find the report in our repo.

Check: Completed, but not fully accurate and/or readable. Requires a bit of detective work on my part to see what you did

Check plus: Hits all the elements. No obvious mistakes. Pleasant to read. No heroic detective work required. Solid.


#### The command below is helpful for debugging, please don't change it

```{r echo=FALSE}
sessionInfo()
```



